Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-01 public/paper/pyg4ometry.tex
latex command for fluka commands (LATTICE COMPOUND etc...)
LATTICE section

@@

\subsection{Lattice}
Description of how we \colorbox{yellow}{translate lattices} 
into one LV with multiple PVs.

>>>>

 % For fluka commands such as LATTICE etc.
\newcommand{\fluka}[1]{\texttt{\MakeUppercase{#1}}}

@@

\subsection{Lattice}

FLUKA supports modular geometries with the use of the \fluka{lattice}
command. Figure~\ref{fig:lattice} demonstrates this capability, and. The
arbitrarily complex \textit{basic unit} can be defined once and used
multiple times by placing one or more empty \textit{lattice cells} with the
associated rototranslation from that \fluka{lattice} cell to the basic
unit. The \fluka{lattice} cells themselves will generally lack structure
and simply serve as a reference to the basic unit. The rototranslated
lattice cell must fully contain the basic unit and all of the regions
within it. When a particle steps into the \fluka{lattice} cell, the
rototranslation is applied to that particle and it is is taken into the
basic unit, and the simulation continues within the basic unit. Any
particles leaving the basic unit will be translated back to the
\fluka{lattice} cell with the inverted rototranslation. Up to two
levels of \fluka{lattice} nesting the are supported in FLUKA.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=6cm]{./diagrams/lattice}
\caption{The \fluka{lattice} feature demonstrating a \fluka{lattice} cell
  referring to its basic unit with the rototranslation $R_\textrm{trans}$.
  Any particle entering the cell will be transformed onto the basic unit
  with $R\textrm{trans}$, and when leaving the basic unit, back to the cell
  with $R_\textrm{trans}^{-1}$.}
\label{fig:lattice}
\end{center}
\end{figure}

This feature is clearly analogous to the logical/physical volume feature in
Geant4, although it is less explicit as the contents of a given logical
volume are clearly stated, whereas the contents of a \fluka{lattice} cell
are implied by the combination of the rototranslation and the locations of
its \fluka{lattice} cell and basic unit.

Translating this construct into a logical volume (basic unit) with many
physical volumes (\fluka{lattice} cells) requires associating each
\fluka{lattice} cell with the full contents of its corresponding basic unit
(typically several regions). This is achieved by meshing the complete
FLUKA geometry and then rototranslating the \fluka{lattice} cell mesh with
its associated rototranslation. By construction this will translate the
\fluka{lattice} cell mesh directly onto the full basic unit mesh. Finally,
in checking for overlaps, the regions within the the basic unit can be
determined. In the final conversion step, the \fluka{lattice} cell can
simply be replaced with a physical volume that refers back to logical
volumes located in the previous step. Thus the \fluka{lattice} cells can
be translated into Geant4's logical/physical volumes. As has been stated,
FLUKA supports two levels of nesting, but currently the conversion to GDML
supports only one. However, extending to an extra level is simple in that
it only involves an extra application of a rototranslation matrix before
checking for overlaps.
